---
name: Trevor
surname: Seeger
qualifications: MDSA MSc
position: "Data Scientist"
address: "Cumming School of Medicine, University of Calgary"
pronouns: "he/him"
phone: +1 403 370 9896
email: "tadam.sgr@gmail.com"
linkedin: "www.linkedin.com/in/trevoraseeger/"
date: "`r Sys.Date()`"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, 
  output_dir = "C:/Users/tadam/OneDrive/Work Related/Job Search 2025") })
output: vitae::hyndman
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(tinytex.verbose = TRUE)
```


```{r}

if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr, tibble, vitae, pkgsearch)

```


# Professional Summary

Experienced Data Scientist and Research Analyst with a strong background in machine learning, statistics, big data, and project management. Adept at converting complex datasets into meaningful insights that drive business improvements and strategic decisions. Strong collaborator with a talent for simplifying intricate concepts for non-technical audiences. Committed to continuous learning and leveraging advanced technologies to address real-world challenges. 




# Technical Skills

- Machine Learning: scikitlearn, pytorch, tensorflow, keras, clustering, dimensionality reduction, neural networks, reinforcement learning. 
- Statistics: Insight generation, ANOVA, linear/polytomous regression, predictive modelling, cross-validation. 
- Software: R, RMarkdown, Python, Git, SQL, MATLAB, SPSS, Tableau, process automation.
- Research: Data integrity and privacy, clinical trials research, research ethics, technical writing, study documentation, knowledge translation, recruitment, and retention.
- Project Management: Personnel management, project lifecycle management, interdisciplinary and multi-team Coordination.




# Projects
```{r}
# https://github.com/TadamSgr/Regressions-Template
# https://github.com/TadamSgr/ML_Templates
```


# Experience

Research Analyst, Data Science Specialist;  The University of Calgary, 2020-Present

- In a Data Scientist role, lead analytics in a health economics research lab where my responsibilities primarily focus on rare diseases and service use across Canada. 
- Develop analysis plans and carry data from collection through to modelling and publication.
- Extract, transform and load complex data, including free text, longitudinal, and clinical data for hundreds of rare disease patients. Codifying clinical data with regular expressions.
- Employed descriptive, classification, regression, and cross-validation models on sparse, longitudinal datasets.



Research Associate; The University of Calgary March 2018 - January 2020 

- Coordinated the daily operations of a multi-university and multi-site clinical research project, collaborating with industry partners: Vivametrica and the Alberta Bone and Joint Health Institute. Priority was to balance stakeholder needs with feasible practices.
- Built, coordinated, and maintained databases, then queried data and performed longitudinal analyses of variance. Presented these queries to stakeholders and laypeople. 


Project Coordinator; The University of Calgary September 2016 - December 2017 

- In a clinical research lab studying adult brain injury and neurorehabilitation, managed ethics and compliance, and conducted recruitment, surveys and follow-ups to ensure minimal attrition (<10%). 
- Advised the team on statistical analyses, authored manuscripts for publication, and coordinated multiple research projects. 
- Collaborated with multiple concurrent research and industry teams. 



# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Master of Data Science & Analytics—Health Data", "2019-2021", "The University of Calgary", "Calgary, Canada",
  "Master of Science—Neurosciences", "2012-2016", "The University of Calgary", "Calgary, Canada",
  "Bachelors of Health Sciences (Honours)", "2007-2011", "The University of Calgary", "Calgary, Canada"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```



# Leadership and Volunteer Experience

Bike Tour Leadership Team – Route Coordinator (2017 – Present)

Branch Out Neurological Foundation

Spearheaded roadside planning and coordination for an annual bike tour involving 200 cyclists. Responsibilities included route planning, building signage, and procuring donations.



# Publications


Degeling K, Tagimacruz T, MacDonald KV, __*Seeger TA*__, Fooks K, Venkataramanan V, Boycott KM, Bernier FP, Mendoza-Londono R, Hartley T, Hayeems RZ, Marshall DA, Care4Rare Canada. Exome Sequencing in the Diagnostic Pathway for Suspected Rare Genetic Diseases: Does the Order of Testing Affect its Cost-Effectiveness? Appl Health Econ Health Policy. 2024 Dec 30. doi: 10.1007/s40258-024-00936-7. Epub ahead of print. PMID: 39739296.

__*Seeger TA,*__ Tabor J, Sick S, Schneider KJ, Jenne C, La P, Talai AS, Rajashekar D, Mouches P, Forkert ND, Emery C, Debert CT. The Association of Saliva Cytokines and Pediatric Sports-Related Concussion Outcomes. J Head Trauma Rehabil. 2020 Sep/Oct;35(5):354-362. doi: 10.1097/HTR.0000000000000605. PMID: 32881769.

King R & __*Seeger TA*__, Wang M, Li Pi Shan R, McGovern C, Knox J, Patel L, Fung T, Sajobi T, Debert C (2020). Early Supported Discharge for Neurorehabilitation Following Acquired Brain Injury. Frontiers in Neurology, 11(November), 1–9. https://doi.org/10.3389/fneur.2020.596526

